### 2022-01-19 paper.tex
conclusion

\textbf{\LARGE Titel der Bachelorarbeit}
%bei langen Titeln, die mehrere Zeilen benoetigen:
%\textbf{\LARGE Langer Titel der  ueber \medskip mehrere Zeilen laeuft}

\bigskip\bigskip
\textbf{Bachelorarbeit}
%bei Masterarbeit:
%\textbf{Masterarbeit}

\bigskip\bigskip\bigskip
Vorgelegt von

\bigskip
\textbf{Vorname Nachname}

\bigskip
aus Geburtsort

\vfill
Angefertigt am\\
Mathematischen Institut\\ 
der Mathematisch-Naturwissenschaftlichen Fakult\"at\\ 
der Heinrich-Heine-Universit\"at D\"usseldorf

\bigskip
%Abgabedatum:
tt.\ Monat jjjj

\bigskip
Betreuer: Prof.\ Dr.\ Vorname Nachname
%Wird der Schwerpunkt der Abschlussarbeit im Anwendungsfach gewaehlt:
%Betreuer: Prof.\ Dr.\ Vorname Nachname\\
%Zweitbetreuer: Prof.\ Dr.\ Vorname Nachname

@@

\section{Conclusion}

\begin{thebibliography}{ccccc}
\addcontentsline{toc}{section}{Literatur}

@@

\end{thebibliography}

%===========================================================
\pagebreak\noindent
\textbf{\LARGE Erkl\"arung}
\addcontentsline{toc}{section}{Erkl\"arung}

\bigskip\bigskip
\noindent 
Hiermit versichere ich, dass ich die   Bachelorarbeit selbst\"andig verfasst und keine
anderen als die angegebenen Quellen und Hilfsmittel benutzt habe.

\bigskip
\noindent
D\"usseldorf, den tt.\ Monat jjjj

\bigskip\bigskip\bigskip
\noindent
(Vorname Nachname)

\end{document}

>>>>

\textbf{\LARGE Spoken Dialog Systems}
%bei langen Titeln, die mehrere Zeilen benoetigen:
%\textbf{\LARGE Langer Titel der  ueber \medskip mehrere Zeilen laeuft}

\bigskip\bigskip
\textbf{Report}
%bei Masterarbeit:
%\textbf{Masterarbeit}

\bigskip\bigskip\bigskip
Written by

\bigskip
\textbf{Hanna Pankova}

\vfill
Faculty of Mathematics and Natural Sciences\\ 
Heinrich Heine University \\
D\"usseldorf

\bigskip
%Abgabedatum:
01 February 2022

\bigskip
Lecturer: Prof.\ Dr.\ Milica Ga\v{s}i\'{c}
%Wird der Schwerpunkt der Abschlussarbeit im Anwendungsfach gewaehlt:
%Betreuer: Prof.\ Dr.\ Vorname Nachname\\
%Zweitbetreuer: Prof.\ Dr.\ Vorname Nachname

@@

\section{Conclusion}
This report gives a brief introduction to the construction of spoken dialog systems. It contains research on different approaches and algorithms used for end-to-end spoken dialog system, that are build via modular approach. Such system was built with the use of different deep learning approaches, all approaches for each of the modules were studied and compared, several dialogs were conducted with the system. The results of the study were described and presented.

\pagebreak
\begin{thebibliography}{ccccc}
\addcontentsline{toc}{section}{Literatur}

@@

\end{thebibliography}
\end{document}
